---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rair

<!-- badges: start -->
[![R-CMD-check](https://github.com/MarkPaulin/rair/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/MarkPaulin/rair/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/MarkPaulin/rair/graph/badge.svg)](https://app.codecov.io/gh/MarkPaulin/rair)
<!-- badges: end -->

This package is a wrapper around Posit's Air R Formatter.

## Installation

You can install the development version of rair like so:

``` r
pak::pkg_install("markpaulin/rair")
```

## Example

`rair` can be used to format R code:

```{r example}
library(rair)
bad_code <- "x+ 1  *(3 -0 )"
cat(format_code(bad_code))
```


## Acknowledgements

This project is a thin wrapper around the [Air](https://github.com/posit-dev/air) formatter. It is heavily dependent on the [rextendr](https://github.com/extendr/rextendr) package, and draws from the [tomledit](https://github.com/extendr/tomledit) package for rust-related inspiration and from [styler](https://github.com/r-lib/styler) for designing an R API for styling code. 
